Data preparation for team category analysis

### 2023-05-11 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Create 02_data_preparation_clusters_team.Rmd
Getting started on team categories data preparation

---
title: "Data preparation for employee category analysis"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "check_in_panel_2023-04-12.rdata"
  unique_identifier_1: !r c("date","person_id")
  date_cohort_month: "2022-03-01"
  observation_window_length_months: 6
---

@@

Collect `person_id` of employees that worked in `r nice_month_year(date_cohort_month_start)`.

```{r}
cohort_ids <- 
  check_in_panel %>% 
  filter(date >= date_cohort_month_start & date <= date_cohort_month_end) %>% 
  select(person_id) %>% 
  distinct()
```

@@

@@

```{r}
prep_building <- 
  cohort_ids
```

@@

Now calculating the number of days per employee by `daily_status_imputed`. Proportions are caluculated for onsite and telework only. The calculations are made in two ways in two ways. First as a proportion of employee working days:

$$
\frac{DailyStatusDays}{WorkingDays}
$$

@@

$$
WorkingDays = OnsiteDays + TeleworkDays
$$

@@

$$
\frac{DailyStatusDays}{ObservationWindowDays}
$$

```{r}
prep_xx <- 
  cohort_panel %>%
  group_by(person_id,daily_status_imputed,.drop = FALSE) %>% 
  summarise(working_days = n_distinct(date)) %>% 
  ungroup() %>% 
  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
  clean_names() %>% 
  rename_with(~glue::glue("daily_status_{.}"), -person_id) %>% 
  mutate(
    working_days = daily_status_reporting_to_job_site + daily_status_teleworking,
    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
  ) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

@@

@@

>>>>

---
title: "Data preparation for team category analysis"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "check_in_panel_2023-04-12.rdata"
  unique_identifier_1: !r c("date","person_id")
  date_cohort_month: "2022-03-01"
  observation_window_length_months: 6
---

@@

Collect `person_id` and `supervisor_e_mail_address` of employees that worked in `r nice_month_year(date_cohort_month_start)`. If a team member had multiple supervisors, select the first one.

```{r}
cohort_ids <- 
  check_in_panel %>% 
  filter(date >= date_cohort_month_start & date <= date_cohort_month_end) %>% 
  arrange(person_id,date) %>% 
  group_by(person_id) %>% 
  summarise(
    supervisor_e_mail_address = first(supervisor_e_mail_address)
  ) %>% 
  ungroup()
```

@@

Check: These have the same number of unique `supervisor_e_mail_address`.

```{r}
cohort_ids %>% 
  summarise(n_distinct(supervisor_e_mail_address)) %>% 
  pull() ==
  cohort_panel %>% 
  summarise(n_distinct(supervisor_e_mail_address)) %>% 
  pull()
```

@@

```{r}
prep_building <- 
  cohort_ids %>% 
  select(supervisor_e_mail_address) %>% 
  distinct()
```

@@

Now calculating the number of days per team by `daily_status_imputed`. Proportions are caluculated for onsite and telework only. The calculations are made in two ways in two ways. First as a proportion of team working days:

$$
\frac{\sum_{m=1}^{x}DailyStatusDays_m}{\sum_{m=1}^{x}WorkingDays_m}
$$

@@

$$
WorkingDays_m = OnsiteDays_m + TeleworkDays_m
$$

$OnsiteDays_m$ is the number of onsite days for team member $m$ and $TeleworkDays_m$ is the number of telework days for team member $m$. $x$ is number of members on team

@@

$$
\frac{\sum_{m=1}^{x}DailyStatusDays_m}{x\times ObservationWindowDays}
$$

```{r}
prep_a <-
  cohort_panel %>%
  group_by(supervisor_e_mail_address,person_id,daily_status_imputed,.drop = FALSE) %>% 
  summarise(working_days = n_distinct(date)) %>% 
  ungroup() %>% 
  filter(
    daily_status_imputed == "Reporting to Job Site" |
      daily_status_imputed == "Teleworking"
  )
```

```{r}
prep_b <- 
  prep_a %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(
    working_days = sum(working_days)
  ) %>% 
  ungroup()
```

```{r}
prep_c <- 
  prep_a %>% 
  group_by(supervisor_e_mail_address,daily_status_imputed) %>% 
  summarise(
    working_days = sum(working_days)
  ) %>% 
  ungroup() %>% 
  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
  clean_names() %>% 
  rename_with(~glue::glue("daily_status_{.}"), -supervisor_e_mail_address)
```

```{r}
prep_d <-
  cohort_panel %>%
  group_by(supervisor_e_mail_address) %>% 
  summarise(
    team_members = n_distinct(person_id)
  ) %>% 
  ungroup()
```

```{r}
prep_e <- 
  prep_b %>% 
  full_join(prep_c) %>% 
  full_join(prep_d)
```

```{r}
prep_xx <- 
  prep_e %>% 
  mutate(
    observation_window_days = team_members*observation_window_days,
    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
  ) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

@@

Check: These have the same number of unique `supervisor_e_mail_address`.

```{r}
cohort_ids %>% 
  summarise(n_distinct(supervisor_e_mail_address)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(supervisor_e_mail_address)) %>% 
  pull()
```

@@

```{r}
prep_building <- 
  prep_building %>% 
  left_join(prep_xx)
```
# CONTINUE FROM HERE
